A simplified dynamic bioenergetic model for coral-algal symbiosis and coral bleaching

### 2016-10-27 JTB_ms/JTB_ms.tex
remake with new sigmaC*

We then specify the input of CO\textsubscript{2} to photosynthesis as
\(j_{CO_2}\), a flux mediated by the host that encompasses potentially
diverse carbon-concentrating mechanisms (CCMs), including active
transport of bicarbonate, carbonic anhydrase-catalyzed conversion of
bicarbonate to CO\textsubscript{2} to promote diffusion toward the
symbiont (Tansik, Fitt, and Hopkinson 2015), and acidification of the
symbiosome to increase localized CO\textsubscript{2} concentrations
around the symbiont (Barott et al. 2014). Since these active CCMs
require energetic input by the host, the magnitude of
CO\textsubscript{2} delivery is proportional to the amount of fixed
carbon available to the host after satisfying its growth demands,
\(j_{eC}\), assuming that some of this carbon is respired to energize
these CCMs. This formulation means that the symbiont indirectly ensures
its own CO\textsubscript{2} supply by providing fixed carbon (=energy)
to the host (Wooldridge 2013), which establishes a positive feedback in
the model that leads to the existence of multiple stable states, which
we discuss below in the context of coral bleaching. The parameter
\(k_{CO_2}\) scales the efficacy of host CCMs, which enables the
comparison of different rates of CO\textsubscript{2} delivery that may
characterize different coral species (Wooldridge 2014a). The input of
CO\textsubscript{2} to the photosynthesis SU is therefore specified as:

@@

Additional metabolic CO\textsubscript{2} recycled from both the host and
symbiont biomass turnover is also made available to the photosynthesis
SU, according to:

\begin{equation} r_{CH}=j_{HT}^0 \cdot {S \over H} \end{equation}\begin{equation} r_{CS}=\sigma_{CS}j_{ST}^0 \end{equation}

>>>>

We then specify the input of CO\textsubscript{2} to photosynthesis as
\(j_{CO_2}\), a flux mediated by the host that encompasses potentially
diverse carbon-concentrating mechanisms (CCMs), including active
transport of bicarbonate, carbonic anhydrase-catalyzed conversion of
bicarbonate to CO\textsubscript{2} to promote diffusion toward the
symbiont (Tansik, Fitt, and Hopkinson 2015), and acidification of the
symbiosome to increase localized CO\textsubscript{2} concentrations
around the symbiont (Barott et al. 2014). Since these active CCMs
require energetic input by the host, the magnitude of
CO\textsubscript{2} delivery is proportional to the amount of fixed
carbon available to the host after satisfying its growth demands,
\(j_{eC}\), assuming that some of this carbon is respired to energize
these CCMs. This formulation means that the symbiont indirectly ensures
its own CO\textsubscript{2} supply by providing fixed carbon (=energy)
to the host (Wooldridge 2013), which establishes a positive feedback in
the model that leads to the existence of multiple stable states, which
we discuss below in the context of coral bleaching. The parameter
\(k_{CO_2}\) scales the efficacy of host CCMs, which enables the
comparison of different rates of CO\textsubscript{2} delivery that may
characterize different coral species (Wooldridge 2014a). The active
input of CO\textsubscript{2} to the photosynthesis SU is therefore
specified as:

@@

An additional fixed proportion of metabolic CO\textsubscript{2}
generated by host biomass turnover is made available to the
photosynthesis SU (scaled to the relative amount of symbiont biomass),
according to:

\begin{equation} r_{CH}=\sigma_{CH}j_{HT}^0 \cdot {S \over H} \end{equation}

along with a fixed proportion of symbiont biomass turnover:

\begin{equation} r_{CS}=\sigma_{CS}j_{ST}^0 \end{equation}

### 2016-10-27 JTB_supp/JTB_supp.Rmd
remake with new sigmaC*

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(message = F, warning = F)
```

@@

par(mfcol=c(6,2), mar=c(2,2,1,4), mgp=c(1,0,0), tcl=0.2)

>>>>

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(message = F, warning = F, echo=F)
```

@@

par(mfcol=c(6,2), mar=c(2,2,1,4), mgp=c(1,0,0), tcl=0.2, xaxs="i")
